---
title: "p8105_hw1_jw4348"
author: "Jingyu Wang"
output: html_document
date: "2023-09-22"
---

```{r, echo = FALSE, message = FALSE}
  library(moderndive)
  library(tidyverse)
```

# Problem 1

Here's a brife description of `early_january_weather` dataset.

* This dataset's _variables_ are **`r ls(early_january_weather)`**.

* The _size_ of the dataset is **`r nrow(early_january_weather)`** rows and **`r ncol(early_january_weather)`** columns.

* The _mean_ of the variable `Temperature` is **`r round(mean(early_january_weather$temp, na.rm = TRUE), digit = 4)`**.

* This is a _scatterplot_ of temperature vs. time in `early_january_weather` dataset

```{r}
hw_plot = ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
hw_plot
```

* Next is the code chunk to export the scatterplot to my project directory.

```{r}
ggsave("scatterplot.pdf", hw_plot)
```

# Problem 2

This code chunk should create a dataframe comprised of: 

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”
  
```{r, hw_df}
  hw_df = 
    tibble(
      num_sample = (rnorm(10)),
      log_vec = num_sample > 0,
      char_vec = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
      fac_vec = factor(c("Agree", "Disagree", "Neutral", "Neutral","Agree", 
                         "Agree","Disagree", "Neutral", "Neutral", "Agree")),
    )
```

Next I will take the _mean_ of each variable in my dataframe `hw_df`.

* The _mean_ of  numeric variable in this data frame is **`r round(mean(pull(hw_df, num_sample)), digit = 4)`**

* The _mean_ of  logical variables in this data frame is **`r round(mean(pull(hw_df, log_vec)), digit = 4)`**

* The _mean_ of  factor variables in this data frame is **`r round(mean(pull(hw_df, fac_vec)), digit = 4)`**

* The _mean_ of  character variables in this data frame is **`r round(mean(pull(hw_df, char_vec)), digit = 4)`**

* After taking the mean of each variables, only **numeric** and **logical** variable works, the **factor** and **character** variables don't work

Finally, I will write a code chunk to convert my other types of variables into numerical one.

```{r, eval=FALSE}
as.numeric(pull(hw_df,log_vec))
as.numeric(pull(hw_df,char_vec))
as.numeric(pull(hw_df,fac_vec))
```

* After I used `as.numeric` to convert my variables: 
  * I got warning messages: 
    * **1: In mean.default(pull(hw_df, fac_vec)) : argument is not numeric or logical: returning NA**
    * **2: In mean.default(pull(hw_df, char_vec)) :argument is not numeric or logical: returning NA**
    
  * Because we were calculating the mean of the numeric versions of factor and character variables, they are not inherently numeric.
  * This do explaining why I got mean for numeric and logical variables but not for factor and character variables previously. Because numeric and logical variables can be treated as numeric. 